---
title: "GSS challange"
author: "Karen Hernandez!"
date: "October 14, 2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
GSS <-read.csv(file="GSScsv.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

Is belief in the bigbang theory (BIGBANG) independent of belief in an afterlife (POSTLIFE)?

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->
```{r}
barchartGC(~POSTLIFE+ BIGBANG,data=GSS)
barchartGC(~POSTLIFE + BIGBANG,data=GSS, type="percent")

```

The graph shows that the amount of people who don't believe in god are much less than the people who do believe in god. As far as the people who believe in the post life there are way more people, and the majority of people who believe in the post life think that the bigbang theory is false. Those who do not believe in the postlife the majority of them think the bingbang is true. of all the people more of them believe in the bigbang theory. There is a statistically significantly difference between believing in the postlife and the bigbang theory. The chart that gives us the biggest impact is the percentage chart which shows that the people who do not believe in the postlife, about 65% believe in the bingbang theory and about 38% do not. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~POSTLIFE + BIGBANG, data=GSS)
rowPerc(table1)
colPerc(table1)
```

34% of people who do not believe in the postlife believe the bigbang is false. About 65% of people who do not believe in postlife believe that the bingbang is true. The people who do believe in the postlife believe that the bigbang is false is about 56%. About 43% of people who believe in the postlife believe that the bigbang is true.


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

Those who believe in postlife, if you do not believe in postlife, what are the odds that the bigbag is false? For thouse who did not beleive in postlife the odds that you said is false, the odds are 8/15. Suppose you did believe in postlife, what are the odds of saying its false? The odds are 88/67. There is not enough data to make a determination on the results. Normally odds are giving .406 : 1. 


```{r}
(8/15)/(88/67)
```



# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

There is not enough data to show, so it will not to let us reject the null hypothesis. So we will be force to say, we fail to reject the null hypothesis. The reason why we are not rejecting it is because of the probability of getting something like this again is 0.8% of the time which is also the P-value.
